---
title: "Individual Assignment: Data Cleaning & Imputation Pipeline in R" 
author: "Nicky Melville"
date: "`r Sys.Date()`"
output:
  word_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(digest)
```

## Objective

This is an individual technical assessment that directly supports the Unit's medium-term goal of establishing an official internal pipeline for data cleaning and imputation, with reproducible reports as a standard deliverable.

## Raw Dataset

Due to the large file size, before running the project, install Git LFS and run:

git lfs install
git lfs pull

## 0. File Configuration

```{r hash-check}
raw_file_path <- "Raw_data/shein_sample.csv"

if (!file.exists(raw_file_path)) {
        stop("The raw data file was not found. Please check that shein_sample.csv is inside the Raw_data folder.")
}

```


---

## 1. Structural Validation

```{r load-data}
#Load Libraries
library(readxl)
library(dplyr)
library(ggplot2)
library(readr)
library(stringr)
library(tidyr)
library(scales)
library(data.table)
library(openxlsx)
library(stringi)
library(lubridate)

#Read in the raw dataset
raw_file <- fread(
        raw_file_path,
        encoding = "UTF-8",
        fill = TRUE,
        quote = "\""
)

raw_file <- as.data.frame(raw_file)

cat("Raw data loaded successfully.\n")
cat("Rows:", nrow(raw_file), "\n")
cat("Columns:", ncol(raw_file), "\n")

#Validating the data compared to the Source Document
dim(raw_file)
names(raw_file)
class(raw_file)

```


---

## 2. Diagnosis and Missing Values

Notable missing columns include Discount, Category and Scraped at. Although "Category" can be substituted to mean other descriptors in the description column. No Category itself is present.
Another notable observation includes scraped_at dates being present in image URLs, including several duplicates within one cell that can be noted.

Most of the Exploratory Diagnosis is exported to Excel file for viewing.

```{r}
# Count records that contain duplicate image URLs


```
---

## 3. Cleaning Log
```{r}


```

---


## 4. Imputation
```{r}


```

---


## 5. Exports
```{r}


```

---


## 6. Summary Statistics (Post-Cleaning)
```{r}


```
