---
title: "Individual Assignment: Data Cleaning & Imputation Pipeline in R" 
author: "Nicky Melville"
date: "`r Sys.Date()`"
output:
  word_document:
    toc: true
    toc_depth: 2
    reference_docx: "report_template.docx" 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(digest)
```

## Objective

This is an individual technical assessment that directly supports the Unit's medium-term goal of establishing an official internal pipeline for data cleaning and imputation, with reproducible reports as a standard deliverable.

## Raw Dataset

The raw dataset is not stored in this GitHub repository because it is larger than GitHub's 100 MB file size limit.

Download the raw file from Google Drive here:
https://drive.google.com/drive/folders/1VQjKMT0UZDbJzx_QmlaUPVwQfFXhHsL-?usp=drive_link

After downloading, place the file in this folder:

Raw_data/shein_sample.csv

## 0. File Configuration

```{r hash-check}
#https://drive.google.com/drive/folders/1VQjKMT0UZDbJzx_QmlaUPVwQfFXhHsL-?usp=drive_link

```


---

## 1. Structural Validation

```{r load-data}
library(readxl)
library(dplyr)
library(ggplot2)
library(readr)
library(stringr)
library(tidyr)
library(scales)

raw_file <- read_csv(raw_data_path)
nrow(raw_file)
ncol(raw_file)
names(raw_file)
head(raw_file)
class(raw_file)
str(raw_file)
summary(raw_file)
```


---

## 2. Diagnosis and Missing Values


---

## 3. Cleaning Log


---


## 4. Imputation


---


## 5. Exports


---


## 6. Summary Statistics (Post-Cleaning)

