---
title: "Individual Assignment: Data Cleaning & Imputation Pipeline in R" 
author: "Nicky Melville"
date: "`r Sys.Date()`"
output:
  word_document:
    toc: true
    toc_depth: 2
    reference_docx: "report_template.docx" 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(digest)
```

## Objective

This is an individual technical assessment that directly supports the Unit's medium-term goal of establishing an official internal pipeline for data cleaning and imputation, with reproducible reports as a standard deliverable.

## Raw Dataset

Due to the large file size, before running the project, install Git LFS and run:

git lfs install
git lfs pull

## 0. File Configuration

```{r hash-check}
raw_file_path <- "Raw_data/shein_sample.csv"

if (!file.exists(raw_file_path)) {
        stop("The raw data file was not found. Please check that shein_sample.csv is inside the Raw_data folder.")
}

```


---

## 1. Structural Validation

```{r load-data}
#Load Libraries
library(readxl)
library(dplyr)
library(ggplot2)
library(readr)
library(stringr)
library(tidyr)
library(scales)
library(data.table)
library(openxlsx)
library(stringi)
library(lubridate)

#Read in the raw dataset
raw_file <- fread(
        raw_file_path,
        encoding = "UTF-8",
        fill = TRUE,
        quote = "\""
)

raw_file <- as.data.frame(raw_file)

cat("Raw data loaded successfully.\n")
cat("Rows:", nrow(raw_file), "\n")
cat("Columns:", ncol(raw_file), "\n")

#Validating the data compared to the Source Document
dim(raw_file)
head(raw_file)
names(raw_file)
class(raw_file)
str(raw_file)
summary(raw_file)
```


---

## 2. Diagnosis and Missing Values

Notable missing columns include Discount, Category and Scraped at. Although "Category" can be substituted to main other descriptors. No Category itself is present.
```{r}
#Exploratory Diagnosis exported to Excel file for viewing.

```
---

## 3. Cleaning Log
```{r}


```

---


## 4. Imputation
```{r}


```

---


## 5. Exports
```{r}


```

---


## 6. Summary Statistics (Post-Cleaning)
```{r}


```
